---
title: "viz_scratch"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(reticulate)
library(sf)
library(plotly)
library(feather)


knitr::opts_chunk$set(echo = F, message = F, warning=F, error=F)
```

## Hypertuning and sequence length

Did a quick grid search of prediction windows and lookback periods to identify best sequence lengths. I'm looking at these from a balance of over fitting vs. test/val performance and training time. Generally speaking smaller, prediction windows lead to better performance, but also longer training times due to more batches. The training logs also look over fit for some combinations.

## Summary table and Figures

labels are I_J where I is total sample length and J is percent of sample predicted on, so 60_0.25 is trained on sequence lengths of 60 with prediction on the last 25% (15) of the sequence (Ignore the ud_dist run for now)

```{r}
files <- list.files('../data/out', full.names = T, recursive = T, pattern = 'test_results.csv')

runs <- files %>% map(~str_split(., '/',5)) %>% flatten() %>% map(.,4) %>% unlist()
runs <- runs[1:9]

reader <- function(id){
  df <- read_csv(grep(paste0(id,'/'), files, value = T),show_col_types = FALSE) %>% mutate(run = id)
}


### Lets look at rmse dist by segment
rmse_by_seg <- function(id){
  print(id)
  df <- reader(id) %>%
    filter(!is.na(temp_ob)) %>%
    group_by(seg_id_nat) %>%
    summarize(count = n(),
          rmse=Metrics::rmse(temp_ob,temp_pred),
          mean_ci = mean(ci_high-ci_low),
          std_ci = sd(ci_high-ci_low)) %>%
    mutate(run = id)
}

run_summaries <- runs %>% map_dfr(rmse_by_seg)

run_summaries_overall <- runs %>% map_dfr(~reader(.) %>% filter(!is.na(temp_ob)) %>% group_by(run) %>%
                                          summarize(rmse=Metrics::rmse(temp_ob,temp_pred),
                                                    median_ci = median(ci_high-ci_low),
                                                    std_ci = sd(ci_high-ci_low)))

########### Train log
files <- list.files('../data/out', full.names = T, recursive = T, pattern = 'train_log.csv')

train_logs <- runs %>% map_dfr(reader)

log_summaries <- train_logs %>%
  group_by(run) %>%
  summarise(mean_epoch_time = mean(time[split=='train']),
            min_val = min(rmse[split=='val']),
            min_val_epoch = epoch[rmse == min_val])
```

#### Bold numbers are **best** models for certain column

```{r}
library(kableExtra)
tableOut <- run_summaries_overall %>%
  left_join(log_summaries) %>%
  mutate(val_test_dif = rmse-min_val) %>%
  mutate_if(is.numeric, ~round(.,2))


styler <- function(col, min =F){
  if(min==T){
    tableOut[[col]] <- cell_spec(tableOut[[col]], bold = ifelse(tableOut[[col]]==min(tableOut[[col]]), T, F))
  }else{
    tableOut[[col]] <- cell_spec(tableOut[[col]], bold = ifelse(tableOut[[col]]==max(tableOut[[col]]), T, F))
  }
  return(tableOut)
}

tableOut <- styler('rmse',T)
tableOut <- styler('median_ci',T)
tableOut <- styler('val_test_dif',T)
tableOut <- styler('mean_epoch_time',T)
tableOut <- styler('min_val',T)

kbl(tableOut, escape = F, align = "c") %>%
  kable_paper("striped", full_width=F) %>%
  add_header_above(c(" ", "Testing" = 3, "Training" = 4))

ggplot(run_summaries, aes(x = rmse)) +
  geom_histogram() +
  geom_vline(aes(xintercept=median(rmse), color = 'Overall Median')) +
  geom_vline(aes(xintercept=mean(rmse), color = "Overalll Mean")) +
  facet_wrap(~run) +
  theme_bw() +
  ggtitle('Test RMSE Across Reaches by Run')

ggplot(run_summaries, aes(x = mean_ci)) +
  geom_histogram() +
  geom_vline(aes(xintercept=median(mean_ci), color = 'Overall Median')) +
  geom_vline(aes(xintercept=mean(mean_ci), color = "Overalll Mean")) +
  facet_wrap(~run) +
  theme_bw() +
  ggtitle('Test Mean PIW Across Reaches by Run')

ggplot(run_summaries, aes(x = std_ci)) +
  geom_histogram() +
  geom_vline(aes(xintercept=median(std_ci, na.rm = T), color = 'Overall Median')) +
  geom_vline(aes(xintercept=mean(std_ci, na.rm=T), color = "Overalll Mean")) +
  facet_wrap(~run) +
  theme_bw() +
  ggtitle('Test SD PIW Across Reaches by Run')


ggplot(train_logs, aes(x = epoch, y=rmse, color = split)) +
  geom_line() +
  scale_color_viridis_d(end=.8) +
  theme_bw() +
  facet_wrap(~run, scales='free') +
  ggtitle('Training Logs')
```

## Exploring Test RMSE and UQ with the 60_0.25 run (PIW = Prediction Interval Width).

```{r cars}
id = '60_0.25'

results <- read_csv(paste0('../data/out/',id,'/test_results.csv')) %>% 
  mutate(within = ifelse(temp_ob > ci_low & temp_pred < ci_high, 'within','not within'),
         piw = ci_high-ci_low)

## Calc percent in CI
print('Percent of test obs in CI')
results %>% filter(!is.na(temp_ob)) %>%
  group_by(within) %>%
  summarise(count = n()) %>%
  mutate(percent = count/(6596+74557))

ci_summary <- results %>% 
  #filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarize(count = n(),
            rmse=Metrics::rmse(temp_ob,temp_pred),
            mean_ci = mean(ci_high-ci_low),
            std_ci = sd(ci_high-ci_low))

bad_ci <- ci_summary %>% filter(mean_ci > 20)

spatial <- readRDS('../data/in/DRB_spatial/network.rds')
edges <- spatial$edges %>% st_as_sf()

seg_plotter_sf <- function(var){
  ci_summary %>%
    filter(mean_ci < 20) %>%
    right_join(edges) %>%
    st_as_sf() %>%
    ggplot(., aes_string(color = var)) +
    geom_sf(size=.75)+
    scale_color_viridis_c(option='inferno', direction=-1, na.value = 'grey80') +
    theme_void() +
    labs(title = var)
}

p2 <- seg_plotter_sf('mean_ci') + ggtitle('Mean Segment PIW \n(Outlier segments not shown)')
p3 <- seg_plotter_sf('std_ci') + ggtitle('Std PIW')
gridExtra::grid.arrange(p2,p3, nrow=1)

ci_summary <- results %>% 
  filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarize(count = n(),
            rmse=Metrics::rmse(temp_ob,temp_pred),
            mean_ci = mean(ci_high-ci_low),
            std_ci = sd(ci_high-ci_low))

p1 <- seg_plotter_sf('rmse') + ggtitle('RMSE')
p4 <- seg_plotter_sf('count') + ggtitle('Num. Obs.') + scale_color_viridis_c(option='plasma', trans = 'log10', na.value='grey80')

gridExtra::grid.arrange(p1,p4, nrow=1)

##
plot_seg_ts <- function(seg_id){
  p <- results %>%
      filter(seg_id_nat == seg_id,
             date > '2011-10-01',
             date < '2016-09-30') %>%
      ggplot(aes(x =date)) +
      geom_point(aes(y=temp_pred, color='Predicted')) +
      geom_ribbon(aes(ymin=ci_low,ymax=ci_high), alpha = .3,color='grey80') +
      geom_point(aes(y=temp_ob,color='Observed'))
  ggplotly(p)
}

ggplot(ci_summary, aes(x=rmse, y = mean_ci)) + geom_point(aes(color=count)) + scale_color_viridis_c(trans='log10') +
  geom_smooth(method='lm', se=F) + 
  ggpmisc::stat_poly_eq(formula= y~x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
  theme_bw() +
  labs(x = 'RMSE', y= 'Mean PIW', color = 'Num Obs (Test)')
```

## Five segments have a UQ interval that is real big (\>20)

Within all of them, the values of at least one input seem pretty far outside the range of the overall distribution. Black lines are distributions for the segments, red lines at bottom are 1st-3rd quartile of overall distribution across all segments. *This is actually pretty cool! Shows that PI3NN is sensitive to noisy inputs and has already helped identify some weird reaches.*

```{r}
sntemp <- read_csv('../data/in/sntemp_inputs_outputs_drb.csv', show_col_types = FALSE) %>%
  select(seg_id_nat, date, seg_rain, seg_tave_air, seginc_swrad, seg_width, seg_length, seginc_potet, seg_slope, seg_humid, seg_elev)

bad_ci_inputs <- sntemp %>% filter(seg_id_nat %in% bad_ci$seg_id_nat)

norm_range <- sntemp %>%
  pivot_longer(-c(seg_id_nat,date)) %>%
  group_by(name) %>%
  summarise(q1 = quantile(value,.25, names = F),
            q2 = quantile(value,.5, names=F),
            q3 = quantile(value, .75, names=F)) %>%
  pivot_longer(-name, names_to = 'quantile')

seg_char_dist <- function(seg){
  bad_ci_inputs %>% filter(seg_id_nat==seg) %>%
    pivot_longer(-c(seg_id_nat, date)) %>%
    ggplot(aes(x=value)) +
    geom_histogram() +
    geom_line(data = norm_range, aes(y=0, color = '1st-3rd quartile')) +
    facet_wrap(~name, scales='free') +
    ggtitle(paste0('Reach: ',seg)) +
    theme_bw() + 
    theme(legend.position = 'None',
          axis.text.x = element_text(hjust = 1, vjust=1, angle = 45))
  }

segs <- unique(bad_ci_inputs$seg_id_nat)

seg_char_dist(segs[1])
seg_char_dist(segs[2])
seg_char_dist(segs[3])
seg_char_dist(segs[4])
seg_char_dist(segs[5])

#gridExtra::grid.arrange(p1,p2,p3,p4,p5, nrow=5)

```

### Check out reservoir impacts

```{r}
seg_atts <- read_feather('../data/in/DRB_spatial/combined_seg_attr_02.feather')

res_info <- readRDS('../data/in/DRB_spatial/segments_relative_to_reservoirs.rds')

# res_info %>% left_join(edges, by='seg_id_nat') %>%
#   st_as_sf() %>%
#   ggplot(aes(color = type_res)) +
#   geom_sf() +
#   theme_void()

res_summ <- results %>%
  filter(!is.na(temp_ob)) %>%
  left_join(res_info) %>%
  group_by(type_res) %>%
  summarise(rmse = Metrics::rmse(temp_ob,temp_pred),
            piw_median = mean(piw),
            piw_sd = sd(piw))


ggplot(res_summ) +
  geom_col(aes(x=type_res, y = rmse)) +
  theme_bw() +
  theme(axis.text = element_text(angle = 45, hjust=1, vjust=1))

ggplot(res_summ) +
  geom_col(aes(x=type_res, y = piw_median)) +
  theme_bw() +
  theme(axis.text = element_text(angle = 45, hjust=1, vjust=1))

ggplot(res_summ) +
  geom_col(aes(x=type_res, y = piw_sd)) +
  theme_bw() +
  theme(axis.text = element_text(angle = 45, hjust=1, vjust=1))

#gridExtra::grid.arrange(p1,p2,p3, ncol=1)

```

## Messing around with the adjacency matrix

```{r, include=F, eval=F, echo=FALSE}
dist <- read_csv('../data/in/distance_matrix_drb.csv')

seg_id_indexes <- dist$from

adp_adj <- read_csv(paste0('../data/out/',id,'/adjmat_out.csv'), show_col_types = FALSE) %>% as.matrix(.)
dimnames(adp_adj) <- list(seg_id_indexes,seg_id_indexes)
adp_adj <- as.data.frame(as.table(adp_adj))

ggplot(adp_adj, aes(x=Var2, y=Var1, fill = Freq)) + geom_raster() +
  scale_fill_viridis_c() +
  theme(axis.text = element_text(angle=45, vjust = 1, hjust =1))


adj_cols <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(cols) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='columns') %>%
  rename(seg_id_nat = cols)


adj_rows <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(rows) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='rows') %>%
  rename(seg_id_nat = rows)

adj_full <- adj_cols %>% bind_rows(adj_rows)

rm(adj_cols, adj_rows)

counts <- results %>%
  filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarise(count = n())

adj_full <- adj_full %>%
  left_join(counts %>% mutate(seg_id_nat = factor(seg_id_nat)))

ggplot(adj_full, aes(x=count)) +
  geom_point(aes(y=mean_dist)) +
  facet_wrap(~vector)

p1 <- adj_full %>%
  filter(vector=='columns') %>%#,
         #mean_ad > .5, count < 500) %>%
  full_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=mean_dist)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value='grey80') +
  theme_void()

p2 <- adj_full %>%
  filter(vector=='columns') %>%
  left_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=count)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value = 'grey80', trans='log10') +
  theme_void()


gridExtra::grid.arrange(p1,p2,nrow=1)

```

```{r}
id <- '60_0.25_ud_dist'
dist <- read_csv('../data/in/distance_matrix_drb.csv') %>% filter(from!= 3558)

seg_id_indexes <- dist$from

adp_adj <- read_csv(paste0('../data/out/',id,'/adjmat_out.csv'), show_col_types = FALSE) %>% as.matrix(.)
dimnames(adp_adj) <- list(seg_id_indexes,seg_id_indexes)
adp_adj <- as.data.frame(as.table(adp_adj))

ggplot(adp_adj, aes(x=Var2, y=Var1, fill = Freq)) + geom_raster() +
  scale_fill_viridis_c() +
  theme(axis.text = element_text(angle=45, vjust = 1, hjust =1))


adj_cols <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(cols) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='columns') %>%
  rename(seg_id_nat = cols)


adj_rows <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(rows) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='rows') %>%
  rename(seg_id_nat = rows)

adj_full <- adj_cols %>% bind_rows(adj_rows)

rm(adj_cols, adj_rows)

counts <- results %>%
  filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarise(count = n())

adj_full <- adj_full %>%
  left_join(counts %>% mutate(seg_id_nat = factor(seg_id_nat)))

ggplot(adj_full, aes(x=count)) +
  geom_point(aes(y=mean_dist)) +
  facet_wrap(~vector)

p1 <- adj_full %>%
  filter(vector=='columns') %>%#,
         #mean_ad > .5, count < 500) %>%
  full_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=mean_dist)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value='grey80') +
  theme_void()

p2 <- adj_full %>%
  filter(vector=='columns') %>%
  left_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=count)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value = 'grey80', trans='log10') +
  theme_void()


gridExtra::grid.arrange(p1,p2,nrow=1)

sntemp_summ <- sntemp %>% distinct(seg_id_nat, .keep_all = T)

adj_full <- adj_full %>% left_join(sntemp_summ %>% mutate(seg_id_nat = factor(seg_id_nat)))

adj_full %>%
  filter(vector=='columns') %>%
  select_if(is.numeric) %>%
  select(adj_value = mean_dist, seg_length, seg_slope, seg_elev, count) %>%
  cor(., use='complete.obs') %>%
  corrplot::corrplot(., type = 'lower')

ggplot(adj_full, aes(x=seg_slope, y =mean_dist)) +
  geom_point() + 
  facet_wrap(~vector)


```
## Sandbox zone

```{r}
results <- read_csv('../data/out/remote/off_test/100_0.1/test_results.csv') %>%
  filter(!is.na(temp_ob))


results <- results %>% group_by(date, seg_id_nat) %>%
  mutate(ob_number = row_number()) %>%
  ungroup()


test_seg <- results %>% filter(seg_id_nat == 2013)


hist(check$ob_number)

results %>% filter(!is.na(temp_ob)) %>% group_by(ob_number) %>%
  summarise(rmse = Metrics::rmse(temp_ob, temp_pred)) %>%
  ggplot(aes(x=ob_number, y=rmse)) + geom_line()

results %>% filter(!is.na(temp_ob)) %>%
  summarise(rmse = Metrics::rmse(temp_ob, temp_pred))

```

```{r}
rm(check
   )
```

