---
title: "viz_scratch"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(reticulate)
library(sf)
library(plotly)
library(feather)


knitr::opts_chunk$set(echo = F, message = F, warning=F, error=F)
```

## Hypertuning and sequence length

Did a quick grid search of prediction windows and lookback periods to identify best sequence lengths. I'm looking at these from a balance of over fitting vs. test/val performance and training time. Generally speaking smaller, prediction windows lead to better performance, but also longer training times due to more batches. The training logs also look over fit for some combinations.

## Summary table and Figures

labels are I_J where I is total sample length and J is percent of sample predicted on, so 60_0.25 is trained on sequence lengths of 60 with prediction on the last 25% (15) of the sequence (Ignore the ud_dist run for now)

```{r}
files <- list.files('../data/out/60_15/', full.names = T, recursive = T, pattern = 'test_results.csv')

runs <- files %>% map(~str_split(., '/')) %>% flatten() %>% map(.,6) %>% unlist()
#runs <- runs[1:9]

reader <- function(id){
  df <- read_csv(grep(paste0(id,'/'), files, value = T),show_col_types = FALSE) %>% mutate(run = id)
}


### Lets look at rmse dist by segment
rmse_by_seg <- function(id){
  print(id)
  df <- reader(id) %>%
    filter(!is.na(temp_ob)) %>%
    group_by(seg_id_nat) %>%
    summarize(count = n(),
          rmse=Metrics::rmse(temp_ob,temp_pred),
          mean_ci = mean(ci_high-ci_low),
          std_ci = sd(ci_high-ci_low)) %>%
    mutate(run = id)
}

run_summaries <- runs %>% map_dfr(rmse_by_seg)

run_summaries_overall <- runs %>% map_dfr(~reader(.) %>% filter(!is.na(temp_ob)) %>% group_by(run) %>%
                                          summarize(rmse=Metrics::rmse(temp_ob,temp_pred),
                                                    median_ci = median(ci_high-ci_low),
                                                    std_ci = sd(ci_high-ci_low)))

########### Train log
files <- list.files('../data/out', full.names = T, recursive = T, pattern = 'train_log.csv')

train_logs <- runs %>% map_dfr(reader)

log_summaries <- train_logs %>%
  group_by(run) %>%
  summarise(mean_epoch_time = mean(time[split=='train']),
            min_val = min(rmse[split=='val']),
            min_val_epoch = epoch[rmse == min_val])
```

#### Bold numbers are **best** models for certain column

```{r}
library(kableExtra)
tableOut <- run_summaries_overall %>%
  left_join(log_summaries) %>%
  mutate(val_test_dif = rmse-min_val) %>%
  mutate_if(is.numeric, ~round(.,2))


styler <- function(col, min =F){
  if(min==T){
    tableOut[[col]] <- cell_spec(tableOut[[col]], bold = ifelse(tableOut[[col]]==min(tableOut[[col]]), T, F))
  }else{
    tableOut[[col]] <- cell_spec(tableOut[[col]], bold = ifelse(tableOut[[col]]==max(tableOut[[col]]), T, F))
  }
  return(tableOut)
}

tableOut <- styler('rmse',T)
tableOut <- styler('median_ci',T)
tableOut <- styler('val_test_dif',T)
tableOut <- styler('mean_epoch_time',T)
tableOut <- styler('min_val',T)

kbl(tableOut, escape = F, align = "c") %>%
  kable_paper("striped", full_width=F) %>%
  add_header_above(c(" ", "Testing" = 3, "Training" = 4))

ggplot(run_summaries, aes(x = rmse)) +
  geom_histogram() +
  geom_vline(aes(xintercept=median(rmse), color = 'Overall Median')) +
  geom_vline(aes(xintercept=mean(rmse), color = "Overalll Mean")) +
  facet_wrap(~run) +
  theme_bw() +
  ggtitle('Test RMSE Across Reaches by Run')

ggplot(run_summaries, aes(x = mean_ci)) +
  geom_histogram() +
  geom_vline(aes(xintercept=median(mean_ci), color = 'Overall Median')) +
  geom_vline(aes(xintercept=mean(mean_ci), color = "Overalll Mean")) +
  facet_wrap(~run) +
  theme_bw() +
  ggtitle('Test Mean PIW Across Reaches by Run')

ggplot(run_summaries, aes(x = std_ci)) +
  geom_histogram() +
  geom_vline(aes(xintercept=median(std_ci, na.rm = T), color = 'Overall Median')) +
  geom_vline(aes(xintercept=mean(std_ci, na.rm=T), color = "Overalll Mean")) +
  facet_wrap(~run) +
  theme_bw() +
  ggtitle('Test SD PIW Across Reaches by Run')


ggplot(train_logs, aes(x = epoch, y=rmse, color = split)) +
  geom_line() +
  scale_color_viridis_d(end=.8) +
  theme_bw() +
  facet_wrap(~run, scales='free') +
  ggtitle('Training Logs')
```

## Exploring Test RMSE and UQ with the 60_0.25 run (PIW = Prediction Interval Width).

```{r cars}
id = '60_0.25'

results <- read_csv(paste0('../data/out/',id,'/test_results.csv')) %>% 
  mutate(within = ifelse(temp_ob > ci_low & temp_pred < ci_high, 'within','not within'),
         piw = ci_high-ci_low)

results <- llo %>% mutate(within = ifelse(temp_ob > ci_low & temp_ob < ci_high, 'within','not within'),
         piw = ci_high-ci_low)

sum(results$within == 'within', na.rm = T)/sum(results$within %in% c('within','not within'), na.rm =T)

## Calc percent in CI
print('Percent of test obs in CI')
results %>% filter(!is.na(temp_ob)) %>%
  group_by(within) %>%
  summarise(count = n()) %>%
  mutate(percent = count/nrow(results %>% filter(!is.na(temp_ob))))

ci_summary <- results %>% 
  #filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarize(count = n(),
            rmse=Metrics::rmse(temp_ob,temp_pred),
            mean_ci = mean(ci_high-ci_low),
            std_ci = sd(ci_high-ci_low))

bad_ci <- ci_summary %>% filter(mean_ci > 20)

spatial <- readRDS('../data/in/DRB_spatial/network.rds')
edges <- spatial$edges %>% st_as_sf()

seg_plotter_sf <- function(var){
  ci_summary %>%
    filter(mean_ci < 20) %>%
    right_join(edges) %>%
    st_as_sf() %>%
    ggplot(., aes_string(color = var)) +
    geom_sf(size=.75)+
    scale_color_viridis_c(option='inferno', direction=-1, na.value = 'grey80') +
    theme_void() +
    labs(title = var)
}

p2 <- seg_plotter_sf('mean_ci') + ggtitle('Mean Segment PIW \n(Outlier segments not shown)')
p2
p3 <- seg_plotter_sf('std_ci') + ggtitle('Std PIW')
gridExtra::grid.arrange(p2,p3, nrow=1)

ci_summary <- results %>% 
  filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarize(count = n(),
            rmse=Metrics::rmse(temp_ob,temp_pred),
            mean_ci = mean(ci_high-ci_low),
            std_ci = sd(ci_high-ci_low))

p1 <- seg_plotter_sf('rmse') + ggtitle('RMSE')
p4 <- seg_plotter_sf('count') + ggtitle('Num. Obs.') + scale_color_viridis_c(option='plasma', trans = 'log10', na.value='grey80')

gridExtra::grid.arrange(p1,p4, nrow=1)

##
plot_seg_ts <- function(seg_id){
  p <- results %>%
      filter(seg_id_nat == seg_id,
             date > '2011-10-01',
             date < '2016-09-30') %>%
      ggplot(aes(x =date)) +
      geom_point(aes(y=temp_pred, color='Predicted')) +
      geom_ribbon(aes(ymin=ci_low,ymax=ci_high), alpha = .3,color='grey80') +
      geom_point(aes(y=temp_ob,color='Observed'))
  ggplotly(p)
}

ggplot(ci_summary, aes(x=rmse, y = mean_ci)) + geom_point(aes(color=count)) + scale_color_viridis_c(trans='log10') +
  geom_smooth(method='lm', se=F) + 
  ggpmisc::stat_poly_eq(formula= y~x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
  theme_bw() +
  labs(x = 'RMSE', y= 'Mean PIW', color = 'Num Obs (Test)')
```

## Five segments have a UQ interval that is real big (\>20)

Within all of them, the values of at least one input seem pretty far outside the range of the overall distribution. Black lines are distributions for the segments, red lines at bottom are 1st-3rd quartile of overall distribution across all segments. *This is actually pretty cool! Shows that PI3NN is sensitive to noisy inputs and has already helped identify some weird reaches.*

```{r}
sntemp <- read_csv('../data/in/sntemp_inputs_outputs_drb.csv', show_col_types = FALSE) %>%
  select(seg_id_nat, date, seg_rain, seg_tave_air, seginc_swrad, seg_width, seg_length, seginc_potet, seg_slope, seg_humid, seg_elev)

bad_ci_inputs <- sntemp %>% filter(seg_id_nat %in% bad_ci$seg_id_nat)

norm_range <- sntemp %>%
  pivot_longer(-c(seg_id_nat,date)) %>%
  group_by(name) %>%
  summarise(q1 = quantile(value,.25, names = F),
            q2 = quantile(value,.5, names=F),
            q3 = quantile(value, .75, names=F)) %>%
  pivot_longer(-name, names_to = 'quantile')

seg_char_dist <- function(seg){
  bad_ci_inputs %>% filter(seg_id_nat==seg) %>%
    pivot_longer(-c(seg_id_nat, date)) %>%
    ggplot(aes(x=value)) +
    geom_histogram() +
    geom_line(data = norm_range, aes(y=0, color = '1st-3rd quartile')) +
    facet_wrap(~name, scales='free') +
    ggtitle(paste0('Reach: ',seg)) +
    theme_bw() + 
    theme(legend.position = 'None',
          axis.text.x = element_text(hjust = 1, vjust=1, angle = 45))
  }

segs <- unique(bad_ci_inputs$seg_id_nat)

seg_char_dist(segs[1])
seg_char_dist(segs[2])
seg_char_dist(segs[3])
seg_char_dist(segs[4])
seg_char_dist(segs[5])

#gridExtra::grid.arrange(p1,p2,p3,p4,p5, nrow=5)

```

### Check out reservoir impacts

```{r}
seg_atts <- read_feather('data/in/DRB_spatial/combined_seg_attr_02.feather')

res_info <- readRDS('data/in/DRB_spatial/segments_relative_to_reservoirs.rds')  %>%
  filter(seg_id_nat != 3558)

f <- function(x,y) ifelse(x==1 & y==1, 1, (x-y)^2)

sim_plotter <- function(i){
  dist = res_info %>%
    mutate(cat = ifelse(type_res %in% i, 1, 0))
  m <- as.matrix(proxy::dist(dist$cat, f)) %>%
    reshape2::melt(.)

ggplot(m, aes(x = Var2, y = -Var1)) + 
  geom_raster(aes(fill=value)) + 
  scale_fill_viridis_c() +
  theme_bw() +
  ggtitle(i)
  }


ids <- unique(res_info$type_res)
#map(ids[1:2], sim_plotter)

adj <- read_csv('data/out/repeat_2/adjmat_out.csv')
#adj <- read_csv('../data/out/off_test/60_10/adjmat_out.csv')
#adj <- read_csv('../data/out/60_0.25_ud_dist/adjmat_out.csv')

sim_plotter_masked <- function(i, adj){
  dist = res_info %>%
    mutate(cat = ifelse(type_res %in% i, 1, 0))
  m <- as.matrix(proxy::dist(dist$cat, f))

  p1 <- as.matrix(adj) %>% reshape2::melt(.) %>%
    #filter(Var1 <50, Var2 <50) %>%
    ggplot(aes(x=Var2, y = Var1)) +
    geom_raster(aes(fill = value)) +
    scale_fill_viridis_c(option='magma') +
    scale_y_reverse(breaks = round(seq(0, 455, by = 20),1)) +
    theme_bw() +
    scale_x_continuous(breaks = round(seq(0, 455, by = 20),1)) +
    theme(legend.position = 'bottom', axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))  
    
  masked <- as.matrix(adj)
  masked[m==0] <- NA

  p2 <- masked %>% reshape2::melt(.) %>%
  #filter(Var1 <50, Var2 <50) %>%
  ggplot(aes(x = Var2, y = Var1)) + 
  geom_raster(aes(fill=value)) + 
  scale_fill_viridis_c(option='magma') +
  scale_y_reverse(breaks = round(seq(0, 455, by = 20),1)) +
  theme_bw() +
  scale_x_continuous(breaks = round(seq(0, 455, by = 20),1)) +
  theme(legend.position = 'bottom', axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
  
  gridExtra::grid.arrange(p1,p2, nrow=1, top = i)
  }

map(ids,~sim_plotter_masked(.,adj))

```


```{r}
check <- as.matrix(dist(res_info$type_res)) #%*% res_info$type_res
check2 <- check %>% reshape2::melt(.)

ggplot(check2, aes(x = Var2, y = Var1)) + 
  geom_raster(aes(fill=value)) + 
  scale_fill_viridis_c() +
  theme_bw() 

res_matrix <- reshape2::dcast(res_info, type_res~type_res)

# res_info %>% left_join(edges, by='seg_id_nat') %>%
#   st_as_sf() %>%
#   ggplot(aes(color = type_res)) +
#   geom_sf() +
#   theme_void()

res_summ <- results %>%
  filter(!is.na(temp_ob)) %>%
  left_join(res_info) %>%
  group_by(type_res) %>%
  summarise(rmse = Metrics::rmse(temp_ob,temp_pred),
            piw_median = mean(piw),
            piw_sd = sd(piw))


ggplot(res_summ) +
  geom_col(aes(x=type_res, y = rmse)) +
  theme_bw() +
  theme(axis.text = element_text(angle = 45, hjust=1, vjust=1))

ggplot(res_summ) +
  geom_col(aes(x=type_res, y = piw_median)) +
  theme_bw() +
  theme(axis.text = element_text(angle = 45, hjust=1, vjust=1))

ggplot(res_summ) +
  geom_col(aes(x=type_res, y = piw_sd)) +
  theme_bw() +
  theme(axis.text = element_text(angle = 45, hjust=1, vjust=1))

#gridExtra::grid.arrange(p1,p2,p3, ncol=1)

```

## Messing around with the adjacency matrix

```{r, include=F, eval=F, echo=FALSE}
dist <- read_csv('data/in/distance_matrix_drb.csv') %>% filter(from != 3558)

seg_id_indexes <- dist$from
id <- 'repeat_2'
adp_adj <- read_csv(paste0('data/out/',id,'/adjmat_out.csv'), show_col_types = FALSE) %>% as.matrix(.)
dimnames(adp_adj) <- list(seg_id_indexes,seg_id_indexes)
adp_adj <- as.data.frame(as.table(adp_adj))

ggplot(adp_adj, aes(x=Var2, y=Var1, fill = Freq)) + geom_raster() +
  scale_fill_viridis_c() +
  theme(axis.text = element_text(angle=45, vjust = 1, hjust =1))


adj_cols <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(cols) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='columns') %>%
  rename(seg_id_nat = cols)


adj_rows <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(rows) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='rows') %>%
  rename(seg_id_nat = rows)

adj_full <- adj_cols %>% bind_rows(adj_rows)

rm(adj_cols, adj_rows)

counts <- results %>%
  filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarise(count = n())

adj_full <- adj_full %>%
  left_join(counts %>% mutate(seg_id_nat = factor(seg_id_nat)))

ggplot(adj_full, aes(x=count)) +
  geom_point(aes(y=mean_dist)) +
  facet_wrap(~vector)

p1 <- adj_full %>%
  filter(vector=='columns') %>%#,
         #mean_ad > .5, count < 500) %>%
  full_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=mean_dist)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value='grey80') +
  theme_void()

p2 <- adj_full %>%
  filter(vector=='columns') %>%
  left_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=count)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value = 'grey80', trans='log10') +
  theme_void()


gridExtra::grid.arrange(p1,p2,nrow=1)

```

```{r}
id <- '60_0.25_ud_dist'
dist <- read_csv('../data/in/distance_matrix_drb.csv') %>% filter(from!= 3558)

seg_id_indexes <- dist$from

adp_adj <- read_csv(paste0('../data/out/',id,'/adjmat_out.csv'), show_col_types = FALSE) %>% as.matrix(.)
dimnames(adp_adj) <- list(seg_id_indexes,seg_id_indexes)
adp_adj <- as.data.frame(as.table(adp_adj))

ggplot(adp_adj, aes(x=Var2, y=Var1, fill = Freq)) + geom_raster() +
  scale_fill_viridis_c() +
  theme(axis.text = element_text(angle=45, vjust = 1, hjust =1))


adj_cols <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(cols) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='columns') %>%
  rename(seg_id_nat = cols)


adj_rows <- adp_adj %>%
  rename(rows = Var1, cols = Var2) %>%
  group_by(rows) %>% 
  summarise(mean_dist = mean(Freq)) %>%
  mutate(vector='rows') %>%
  rename(seg_id_nat = rows)

adj_full <- adj_cols %>% bind_rows(adj_rows)

rm(adj_cols, adj_rows)

counts <- results %>%
  filter(!is.na(temp_ob)) %>%
  group_by(seg_id_nat) %>%
  summarise(count = n())

adj_full <- adj_full %>%
  left_join(counts %>% mutate(seg_id_nat = factor(seg_id_nat)))

ggplot(adj_full, aes(x=count)) +
  geom_point(aes(y=mean_dist)) +
  facet_wrap(~vector)

p1 <- adj_full %>%
  filter(vector=='columns') %>%#,
         #mean_ad > .5, count < 500) %>%
  full_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=mean_dist)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value='grey80') +
  theme_void()

p2 <- adj_full %>%
  filter(vector=='columns') %>%
  left_join(edges %>% mutate(seg_id_nat= factor(seg_id_nat))) %>%
  st_as_sf() %>%
  ggplot(aes(color=count)) +
  geom_sf() +
  scale_color_viridis_c(option = 'inferno', na.value = 'grey80', trans='log10') +
  theme_void()


gridExtra::grid.arrange(p1,p2,nrow=1)

sntemp_summ <- sntemp %>% distinct(seg_id_nat, .keep_all = T)

adj_full <- adj_full %>% left_join(sntemp_summ %>% mutate(seg_id_nat = factor(seg_id_nat)))

adj_full %>%
  filter(vector=='columns') %>%
  select_if(is.numeric) %>%
  select(adj_value = mean_dist, seg_length, seg_slope, seg_elev, count) %>%
  cor(., use='complete.obs') %>%
  corrplot::corrplot(., type = 'lower')

ggplot(adj_full, aes(x=seg_slope, y =mean_dist)) +
  geom_point() + 
  facet_wrap(~vector)


```
## Sandbox zone


```{r}
### Let's just look at the 60 because it's more comparable in terms of number of training sequences
results <- read_csv('../data/out/off_test/60_10/test_results.csv') %>%
    group_by(date, seg_id_nat) %>%
    mutate(ob_number = row_number()) %>% ungroup() %>%
    group_by(ob_number) %>%
    summarise(rmse = Metrics::rmse(temp_ob, temp_pred))

end_preds <- run_summaries_overall %>% filter(run == '60_0.25_ud_dist')

ggplot(results, aes(x=ob_number,y=rmse)) +
  geom_line() +
  geom_hline(aes(yintercept=end_preds$rmse[1]))
```




```{r}
files <- list.files('../data/out/off_test', full.names = T, recursive = T, pattern = 'test_results.csv')

reader <- function(id){
  df <- read_csv(grep(paste0(id,'/'), files, value = T), show_col_types = FALSE) %>% 
    group_by(date, seg_id_nat) %>%
    mutate(ob_number = row_number()) %>% ungroup() %>%
    group_by(ob_number) %>%
    summarise(rmse = Metrics::rmse(temp_ob, temp_pred)) %>%
    mutate(run = id) 
}

runs <- c('60_10','100_10','365_10','200_10', '200_long')

og_renamed <- run_summaries_overall %>%
  filter(run %in% c('60_0.25_ud_dist')) %>%
  mutate(og=case_when(grepl('_0.1', run) ~ '0.1', grepl('_0.25',run)~'0.25',grepl('_1',run)~'1'),
         run=case_when(grepl('100_',run)~'100_10',grepl('60_',run)~'60_10')) %>%
  filter(!is.na(run))
         
rmse_by_ob_position <- runs %>% map_dfr(reader)

rmse_by_ob_position %>%
  group_by(run) %>%
  mutate(ob_number = (max(ob_number)-ob_number)*10) %>%
  ungroup() %>%
  ggplot(aes(x=ob_number, y=rmse)) + geom_line() +
  geom_hline(data=og_renamed, aes(yintercept=rmse, color=og)) +
  labs(x = 'Observation location in sequence', color = 'Runs trained on\nend of seq preds') +
  facet_wrap(~run, scales = 'free_x') +
  theme_bw()


results %>% filter(!is.na(temp_ob)) %>%
  summarise(rmse = Metrics::rmse(temp_ob, temp_pred))
```



```{r}
reader <- function(id){
  df <- read_csv(grep(paste0(id,'/'), files, value = T),show_col_types = FALSE) %>% mutate(run = id)
}


runs <- c('60_10','100_10','365_10','200_10','200_long')

########### Train log
files <- list.files('../data/out/off_test', full.names = T, recursive = T, pattern = 'train_log.csv')


train_logs <- runs %>% map_dfr(reader)

log_summaries <- train_logs %>%
  group_by(run) %>%
  summarise(mean_epoch_time = mean(time[split=='train']),
            min_val = min(rmse[split=='val']),
            min_val_epoch = epoch[rmse == min_val])


ggplot(train_logs, aes(x = epoch, y=rmse, color = split)) +
  geom_line() +
  scale_color_viridis_d(end=.8) +
  theme_bw() +
  facet_wrap(~run, scales='free') +
  ggtitle('Training Logs')

```

### Take a look at some time series

```{r}
reader <- function(id){
  df <- read_csv(grep(paste0(id,'/'), files, value = T),show_col_types = FALSE) %>% mutate(run = id)
}

runs <- c('200_10')

########### Train log
files <- list.files('../data/out/off_test', full.names = T, recursive = T, pattern = 'test_results.csv')

test_segs <- c('1450','1462')

results <- runs %>% map_dfr(reader) %>%
  filter(seg_id_nat %in% test_segs) %>%
  group_by(date, seg_id_nat) %>%
  mutate(ob_number = row_number()) %>% ungroup() %>%
  filter(ob_number %in% c(min(ob_number), max(ob_number))) %>%
  mutate(pred_type = factor(ob_number, labels = c('Late Sequence Pred', 'Early Sequence Pred'))) %>%
  select(-ob_number) %>%
  pivot_wider(names_from = pred_type, values_from = temp_pred) %>%
  pivot_longer(c(`Late Sequence Pred`, `Early Sequence Pred`, temp_ob))




results %>% filter(seg_id_nat %in% test_segs,
                   date > '2010-01-01') %>%
  ggplot(aes(x=date, y = value, color = name)) +
  geom_line(alpha = .5) +
  scale_color_viridis_d(option='plasma', end = .8) +
  facet_wrap(~seg_id_nat,nrow=2) +
  theme_bw()


```

#### Reach Plotter

```{r}
baseline <- reader('6_2', list.files('../data/out/hypertuning_kernel_layer/60_15', full.names = T, recursive = T, pattern = 'test_results.csv'))

llo <- view_test_results('../data/out/llo')
llo_groups <- read_csv('../data/in/DRB_spatial/llo_groups.csv') %>%
    mutate(run = paste0('group_',test_group)) %>% select(run, seg_id_nat)
llo <- llo %>% inner_join(llo_groups)

reach_plotter <- function(reaches, date_start,date_end, df){
  nreaches <- length(reaches)
  
  df %>% filter(seg_id_nat %in% reaches,
                date >= date_start, date <= date_end) %>%
    mutate(ci_low = ifelse(ci_low < 0, 0, ci_low)) %>%
    ggplot(aes(x = date)) +
    geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .2) +
    geom_point(aes(y=temp_pred, color = "Predicted"), size = .6, alpha = .2) +
    geom_point(aes(y=temp_ob, color = "Observed"), size = .6, alpha = .2) +
    scale_color_viridis_d(begin =.3, end = .6) +
    facet_wrap(~seg_id_nat, nrow = nreaches, scales = 'free') +
    theme_bw() +
    labs(x = 'Date', y = 'Temperature (°C)')
}

reach_plotter(c(1498,1565),'2011-10-01','2016-09-30', llo)


```

